Information Disclosure in Dynamic Innovation Contests

### 2025-06-04 paper/Paper.tex
update

This paper focuses on the two players innovation contest with a continuous time  where the players’ relative position is public information throughout the game.
This is closely related to tug-or-war contest, which, to our knowledge, was first formally given by \citet{Harris1987Race} as a one-dimensional simplification of the multi-stage R\&D race. 
The output processes are model by Brownian motions drifted with effort inputs, which is followed by \cite{budd1993model} who model the state of a dynamic competition of two innovative duopoly firms by a Brownian motion drifted by the effort gap, and solve the equilibrium approximately. 
Furthermore, \citet{Moscarini2011Contest} model the tug-of-war state as the gap of the two outputs directly, and draw an analytical equilibrium of the pure strategies.

...

Information disclosure in contest - \cite{Bimpikis2019Contest}.

...

Closest paper - \cite{ryvkin2022fight}.

...

Structural Estimation:

- dynamic: \cite{jiang2022role}.

- static: \cite{huang2021structural}, \cite{shakhgildyan2022nonparametric}, 
\cite{yoganarasimhan2016estimation}

- kaggle: \cite{lemus2021dynamic}

\cite{chen2021attracting}, \cite{zhang2019structural}

@@

\begin{algorithm}[H]
\caption{Synthetic Data Simulation}
\label{algo-dgp}
\begin{algorithmic}
\STATE \textbf{Input:} 
	$\Delta$, $T$, $c_i$, $c_j$, $\sigma$, $\lambda$, $r$, $\tau^\star$, $y_0$, $\mu_0$
\STATE Sample $\{s_k^{i(j)}\}^{N_{i(j)}}_{k=1}$ from Poisson process $(\tau^\star)$ on $[0, T)$
\STATE Sample $\{u_k^{i(j)}\}^{N_{i(j)}}_{k=1}$ from uniform distribution on $[0, 1]$
\STATE Sample series of Brownian motions $(W_t)$ and $(B_t)$
\STATE Initialize $\ell^{i(j)}=0$, $\hat{y}_0 = 0$, $\tilde{y}_t=\mu_0$
\FOR{$t = 0$ to $T$}
    \STATE $m_{i(j)}(\tilde{y}_t, t)$  $\gets$ (\ref{eq-equilibrium-effort}), $\tau^{i(j)}(t)$ $\gets$ (\ref{eq-model-intensity})
    \hfill \COMMENT{Use $\theta$, $c_{i(j)}$, $\sigma$, $r$, $T$}
    \STATE $y_{t+\Delta} \gets$ (\ref{eq-state-dynamics}); $\tilde{y}_{t+\Delta}$ $\gets$ (\ref{eq-fintered-y-update})
    \hfill \COMMENT{Use $\sigma$, $\lambda$, $\Delta$, $W_{t+\Delta}$, $y_0$}
    \FOR{$s_{k}^{i(j)} \in [t, t+\Delta)$} 
        \IF {$u_k^{i(j)} < \tau_{i(j)}(s_{k}^{i(j)}) / \tau^\star_{i(j)}$}
        	    \STATE $\hat{t}^{i(j)}_{\ell} \gets s_{k}^{i(j)}$; $\ell^{i(j)} \gets \ell^{i(j)}+1$
	    \hfill \COMMENT{Accept the submission event}
	    \STATE $\hat{y}_{t+\Delta} \gets $ (\ref{eq-leaderboard-gap})
	    \hfill \COMMENT{Use $\sigma$, $\lambda$, $B_{t+\Delta}$}
        \ENDIF
    \ENDFOR
\ENDFOR
\STATE \textbf{Output:} $(y_t)$, $(\tilde{y}_t)$, $(m_{i(j)}(\tilde{y}_t, t))$, $\{\hat{t}_k^{i(j)}\}^{N_{i(j)}}_{k=1}$, $(\hat{y}_{t_k})_{k=1}^{N_i + N_j}$
\end{algorithmic}
\end{algorithm}

>>>>

This study is closely related to the below strands of literature:

\subsubsection{Contest Design.}

%% Static Contest Design
% definition
A rich literature on \textit{static} contest design \citep{Ales2017Contest} investigates how to structure competitive environments to elicit optimal performance. 
These models typically rely on an explicit contest success function (CSF) that maps individual effort to winning probabilities \citep{skaperdas1996contest}.\footnote{There are exceptions like beauty or barrier contests.} 
Early contributions include \citet{Tullock1980}, \citet{Lazear1981tournaments}, and \citet{nalebuff1983Competition}. 
% application
This line of research is motivated by a wide range of real-world applications, including CEO selection \citep{tsoulouhas2006ceo}, beauty contests \citep{morris2002social}, election campaigns \citep{denter2020campaign}, advertising \citep{dockner2018Advertising}, litigation \citep{baik2007litigation, park2022litigation}, and innovation tournaments \citep{chen2021DataSharing}.
% design
Key design dimensions studied in the literature include optimal prize allocation \citep{moldovanu2001optimal, ales2017optimal_award}, participation rules \citep{Ales2021Innovation, stouras2022role}, contest duration\footnote{Static model in the sense that homogeneous participants make a single submission at the contest deadline, with no intermediate feedback provided throughout the process.} \citep{korpeoglu2021duration}, ex-ante handicapping of heterogeneous agents \citep{tsoulouhas2006ceo, kirkegaard2012favoritism, syam2013sales}, mechanisms addressing ex-post outcome imbalances \citep{Imhof2016Ex_post}, and information disclosure in auction-like environments \citep{bergemann2022optimal, antsygina2023optimal}.

%% Dynamic Contest Design
% Transition
While these studies offer valuable insights into incentive design, they largely overlook how participants dynamically adjust their efforts in response to evolving competition.
% Dynamic Contest
In contrast, this paper focuses on \textit{dynamic} contests, where strategic decisions unfold over time.
Two main modeling approaches have been used to capture such dynamic strategic interactions:

% One Way: Poisson Arrival of Innovation Success
One strand of the literature models dynamic contests as multistage processes, where participants exert effort over time while facing uncertainty about intermediate progress.
This structure facilitates the analysis of the mid-contest policy instruments available to the contest designer, such as feedback disclosure, screening mechanisms, etc.
Specifically, in a typical two-stage setting \citep{aoyagi2010information, mihm2019feedback}, the initial stage captures either feasibility uncertainty or foundational experimentation, with progress revealed through milestone feedback provided by the contest organizer. 
Participants exert effort in both stages, and the final output reflects the cumulative impact of early performance and subsequent improvement.
Similarly, \citet{Bimpikis2019Contest} study a two-stage model in which agents exert continuous effort to complete Stage A (potentially infeasible) and Stage B (feasible), with breakthroughs governed by Poisson processes.
In all these models, the contest designer may strategically disclose interim feedback.
Another example is \citet{Khorasani2023screening}, who analyze a two-stage contest in which solvers invest exploratory effort to generate viable ideas, with only those passing an imperfect screening mechanism proceeding to execution.

% Another Way of Modelling
The second approach, more closely related to our work, treats output as a stochastic process whose drift depends on the participant’s effort.
This line of research originates from the tug-of-war framework, first formalized by \citet{Harris1987Race} as a one-dimensional simplification of a multi-stage R\&D race.
Subsequent studies build on this foundation by modeling each player’s progress as a Brownian motion.
\citet{budd1993model}, for example, analyze a duopoly innovation race where the state evolves as a Brownian motion driven by the difference in effort, and characterize an approximate equilibrium.
\citet{Moscarini2011Contest} advance this approach by modeling the game state as the output gap between players and derive closed-form equilibrium strategies under pure-strategy play.
\citet{ryvkin2022fight} adapt their framework to a dynamic contest with a fixed deadline, providing a closed-form solution for the Markov perfect equilibrium.

%% Online Crowdsourcing
% this paper
This paper studies online crowdsourcing contests, which are typically characterized by 
$i$) fixed deadlines, 
$ii$) repeated submissions, and 
$iii$) public real-time feedback,
all governed by platform-specific rules and evaluation metrics.
% our foundation
Hence, our analysis builds on the model by \citet{ryvkin2022fight}, which, despite its simplifications, offers a closed-form solution that balances realism with analytical tractability. 
To better reflect the dynamics of online leaderboards, we depart from their full-information setting by introducing a noisy real-time public signal, thereby enhancing the model’s empirical relevance.

\subsubsection{Structural Estimation of Contests.}

Beyond theoretical modelling, a growing body of research employs structural estimation techniques to recover key parameters of contest environments using observed data.

% Static contests
In the structural estimation of static contests, when a contest success function (CSF) is explicitly specified, the primary goal is to estimate its functional form or key parameters \citep{hwang2012technology, kang2016policy, huang2021structural}.
In contrast, for contests without a well-defined or smooth CSF—such as beauty contests—researchers typically rely on equilibrium conditions, most notably the first-order condition.
For example, \citet{yoganarasimhan2016estimation} proposes a two-step semiparametric estimator, resembling the EM algorithm, to recover both unobserved auction heterogeneity and bidder cost distributions.
Similarly, in auction-like models \citep{guerre2000optimal, shakhgildyan2022nonparametric}, nonparametric estimation of the underlying valuation structure often serves as a first step, providing the foundation for subsequent structural estimation.

% Dynamic contests
Most dynamic structural estimations rely on the Markov Perfect Equilibrium (MPE) of a dynamic game. 
However, when the model is calibrated to closely fit real-world data, the MPE typically lacks a closed-form solution.
For example, \citet{jiang2022role} develop a finite-horizon dynamic game with discrete time, state, and action spaces to model creators’ strategic behaviour in response to feedback during online logo design contests.
Using data from 810 contests, they implement a two-step maximum likelihood estimation (MLE) procedure under the assumption of ex-ante homogeneous contests and players: the first step estimates action-specific state transition probabilities, while the second recovers utility parameters.

Specific to online crowdsourcing environments, 
\citet{chen2021attracting} use data from 1,980 contests on TaskCN.com to examine how contest duration affects both the number and quality of participants.
Through regression analysis, they show that while longer durations attract more contestants, they tend to reduce the quality of top entrants.
\citet{zhang2019structural} build a dynamic structural model to study how participants in crowdsourcing contests learn and choose contests over time.
Their model shows that competing against superstars accelerates learning by providing more informative feedback.
Using Bayesian updating and a hierarchical model, they estimate how individuals trade off monetary rewards, learning opportunities, and participation costs, based on data from Topcoder.

Closely related to our work, \citet{lemus2021dynamic} conduct contest-level structural estimation using Kaggle data.
They propose a finite-horizon dynamic game in which, after each submission, players decide whether to continue or exit, essentially solving an optimal stopping problem.
Players can only make this decision immediately after completing a submission, which arrives at random intervals and incurs a privately drawn cost.
Their estimation proceeds in two stages: the first uses maximum likelihood and the EM algorithm to estimate primitive parameters such as the distribution of player types and scores; the second applies a CCP-based estimator to identify the cost distribution.
Our model differs in two key respects: 
(1) we treat submissions as the outcome of accumulative effort rather than discrete costly actions—an assumption that better reflects actual player behaviour; and
(2) we explicitly model belief updating from signals to identify structural parameters, whereas their CCP-based method relies on a coarser behavioural approximation.

The structure of the paper is as follows: 
Section~\ref{contest-theory} introduces our theoretical model of online crowdsourcing contests. 
Section~\ref{sect-bayes-framework} presents the Bayesian estimation framework. 
In Section~\ref{sect-synthetic}, we describe the data-generating process and apply the Bayesian framework to synthetic data. 
Section~\ref{sec-kaggle-application} validates the theoretical model using real-world data. 
All code and implementation details are available on GitHub.

@@

\begin{algorithm}[!ht]
\caption{Synthetic Data Simulation}
\label{algo-dgp}
\begin{algorithmic}
\STATE \textbf{Input:} 
	$\Delta$, $T$, $c_i$, $c_j$, $\sigma$, $\lambda$, $r$, $\tau^\star$, $y_0$, $\mu_0$
\STATE Sample $\{s_k^{i(j)}\}^{N_{i(j)}}_{k=1}$ from Poisson process $(\tau^\star)$ on $[0, T)$
\STATE Sample $\{u_k^{i(j)}\}^{N_{i(j)}}_{k=1}$ from uniform distribution on $[0, 1]$
\STATE Sample series of Brownian motions $(W_t)$ and $(B_t)$
\STATE Initialize $\ell^{i(j)}=0$, $\hat{y}_0 = 0$, $\tilde{y}_t=\mu_0$
\FOR{$t = 0$ to $T$}
    \STATE $m_{i(j)}(\tilde{y}_t, t)$  $\gets$ (\ref{eq-equilibrium-effort}), $\tau^{i(j)}(t)$ $\gets$ (\ref{eq-model-intensity})
    \hfill \COMMENT{Use $\theta$, $c_{i(j)}$, $\sigma$, $r$, $T$}
    \STATE $y_{t+\Delta} \gets$ (\ref{eq-state-dynamics}); $\tilde{y}_{t+\Delta}$ $\gets$ (\ref{eq-fintered-y-update})
    \hfill \COMMENT{Use $\sigma$, $\lambda$, $\Delta$, $W_{t+\Delta}$, $y_0$}
    \FOR{$s_{k}^{i(j)} \in [t, t+\Delta)$} 
        \IF {$u_k^{i(j)} < \tau_{i(j)}(s_{k}^{i(j)}) / \tau^\star_{i(j)}$}
        	    \STATE $\hat{t}^{i(j)}_{\ell} \gets s_{k}^{i(j)}$; $\ell^{i(j)} \gets \ell^{i(j)}+1$
	    \hfill \COMMENT{Accept the submission event}
	    \STATE $\hat{y}_{t+\Delta} \gets $ (\ref{eq-leaderboard-gap})
	    \hfill \COMMENT{Use $\sigma$, $\lambda$, $B_{t+\Delta}$}
        \ENDIF
    \ENDFOR
\ENDFOR
\STATE \textbf{Output:} $(y_t)$, $(\tilde{y}_t)$, $(m_{i(j)}(\tilde{y}_t, t))$, $\{\hat{t}_k^{i(j)}\}^{N_{i(j)}}_{k=1}$, $(\hat{y}_{t_k})_{k=1}^{N_i + N_j}$
\end{algorithmic}
\end{algorithm}
